TacticToe: Learning to Prove with Tactics

### 2018-02-20 tactictoe_jv.tex
abstract

\todoi{JU review: Still feels more like an intro than an abstract. Could be
shorter and punchier.}

\todoi{Move part of the abstract to the introduction.}
\begin{abstract}

We implement a tactical prover TacticToe on top of the HOL4 interactive theorem 
prover. TacticToe learns from many human proofs which mathematical method is 
useful in particular proof situations.
This knowledge is then used in a Monte Carlo tree search algorithm that 
explores the most promising tactic-level proof paths.
On a single CPU, with a time limit of 60 seconds, TacticToe proves 66.4\% of 
7164 theorems in HOL4's standard library whereas
Eprover solves 34.5\%. The success rate rises to 69.0\% by combining the
results of \tactictoe and \eprover.
\end{abstract}

>>>>

\begin{abstract}
We implement a tactical prover TacticToe on top of the HOL4 interactive theorem 
prover. TacticToe learns from human proofs which mathematical method is 
useful in a particular proof situation.
This knowledge is then used in a Monte Carlo tree search algorithm that 
explores the most promising tactic-level proof paths.
On a single CPU, with a time limit of 60 seconds, TacticToe proves 66.4\% of 
7164 theorems in HOL4's standard library whereas
Eprover solves 34.5\%. The success rate rises to 69.0\% by combining the
results of TacticToe and Eprover.
\end{abstract}
